Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-28 colt-21/cvx-flats.tex
intro

\raf{\hrule Old version below:}

Surrogate risk minimization is one of the most widespread learning heuristics in supervised machine learning.
%A surrogate loss is often necessary for one of two reasons: (1) the target loss does not satisfy some desiderata, such as convexity, or (2) the target loss may not be given at all, as is often the case in continuous estimation problems, when one instead has a target conditional statistic to estimate from training data.
We require surrogate losses to be \emph{consistent}, which informally means the surrogate loss ``corresponds'' to the desired learning problem, and this condition is a prerequisite for deriving excess risk bounds.
%Deriving excess risk bounds and rates require a surrogate to be consistent, hence the focus on consistency.
Construction of surrogates for a desired task is often ad hoc, leaving consistency of such losses an open question.
Depending on the data distribution, these inconsistent surrogates may actually yield predictions that do not correspond to the target task. 
The characterizations and constructions of efficient surrogates for a given task would allow for us to easily test the consistency of a surrogate for a given task. \jessiet{Not quite what we want to say- can someone refine this?}
%Roughly speaking, consistency means that minimizing surrogate risk corresponds to solving the target problem of interest: the target risk should also be minimized, or the average deviation from the true conditional statistic function converges to 0.\jessie{Not sure if I like these sentences here, or in general}

%examples of problems where we care a lot about prediction dimension (that happen to be finite discrete)
A variety of prediction tasks call for the construction of consistent, and ideally convex, surrogates.
Applications ranging from extreme classification to top-$k$ predictions to ranking have inspired an entire line of research into the construction of surrogate loss functions for such discrete tasks.
The dimensionality of this surrogate prediction space often scales linearly with the number of outcomes unless sacrifices are made in terms of consistency if one is not careful.
This linear growth of prediction dimension (in the number of outcomes) leads to computationally expensive or intractable optimization problems, but it is unknown in many cases if this linear scaling in dimensionality is necessary for a consistent surrogate.
Tight bounds on the dimension of the prediction space for a consistent convex surrogate remain an open question, though we tighten currently known bounds in this work.

For some tasks, it is possible to reduce the dimension of this surrogate prediction space without sacrificing consistency.  
Consider the high-confidence classification presented by the abstain target loss~\citep{ramaswamy2012classification,ramaswamy2018consistent}.
When trying to predict one of $n$ outcomes, the abstain loss is minimized by predicting the most likely outcome if it is likely enough, and ``abstaining'' from predicting otherwise.
\citet{ramaswamy2016convex} present a convex surrogate, called the BEP loss, for the abstain target loss that takes as input a prediction whose dimension is logarithmic in the number of outcomes.
The BEP loss is a high-dimensional generalization of the hinge loss so that outcome predictions are ``embedded'' into the corners of the $\pm 1$ hypercube, and abstaining is embedded to the origin.
This BEP loss is consistent with respect to the target 0-1 modification $\ell^{abs}(r,y) = \Ind{r \not \in \{y,\bot\}} + (1/2) \Ind{r = \bot}$, and takes $\Theta(\log n)$-dimensional surrogate predictions, instead of $\Theta(n)$, as was used by previous consistent surrogates, e.g.~\citet{crammer2001algorithmic}.

%in a seemingly unrelated setting, finance problems blah blah.
In a seemingly unrelated problem, financial institutions have sought scoring rules to learn banks' estimates of financial risk in their investments.\jessie{cite}
Given the desired measure of financial risk, such as the variance or Conditional Value at Risk (CVaR), auditing institutions are tasked with designing scoring rules that, directly or indirectly, incentivize truthfully estimating the desired statistic.
For example, while there is no loss function that enables one to directly learn the variance, we can learn the first and second central moments \jessiet{how much detail to share?} by proper scoring rules, which yields an unbiased estimator of the variance.
However, asking a bank for a large number of predictions may be infeasible by their own knowledge of the financial risk distribution.
That is, institutions and individuals might only be reasonably expected to articulate summary statistics of their beliefs, rather than their entire belief distribution.
To this end, learning desired statistics with a minimal number of reports also emerges as an important question in finance.
\jessie{Raf, helppp}

% point out distinctions and how these seem like very different settings (e.g. loss vs no loss), but we'll be able to address both with the same techniques, modulo some simplicity in the proofs.
Despite their seeming differences, in this paper, we show formal connections between consistent surrogates and property elicitation, and leverage these to understand new bounds on prediction dimension for consistent surrogates that spans both settings. 
Reducing surrogate prediction dimension while maintaining consistency is important to improve the computational complexity of the learning algorithm, as it decreases the dimension of the ERM optimization problem.
Given a target loss or statistic, we provide a new framework for constructing lower bounds on this prediction dimension that supersedes previous results in the machine learning literature (Corollary~\ref{cor:fsd-bound}) and answers open questions of the elicitation literature (\cite{frongillo2020elicitation}).

@@

\begin{figure}[ht]
\begin{minipage}{0.45\linewidth}
	\centering
	\includegraphics[width=\linewidth]{tikz/fsd-bound.pdf}
	\caption{%Since the uniform distribution is in the relative interior of the simplex and the level set $\gamma_\bot$, 
          $\dim(\Sc_{\gamma_\bot}($\textbullet$)) = 2$ and $\dim(\Sc_{\gamma_\bot}({\color{blue}\star})) = 1$.
          \raf{I had a feeling my comment wasn't 100\% clear -- fine/useful to have the color, but good to have the symbol in case of colorblindness/grayscale}
          \vspace*{-5pt}        }
	\label{fig:fsd-bound}
\end{minipage}
\hfill
\begin{minipage}{0.45\linewidth}
	\centering
	\includegraphics[width=\linewidth]{tikz/flats-bound.pdf}
	\caption{Any $1$-flat $F$ through \textbullet leaves $\gamma_\bot$.
	However, there is a $1$-flat containing ${\color{blue}\star}$ that is a subset of $\gamma_\bot$ and $\gamma_3$.
	}
	\label{fig:flats-bound}
\end{minipage}
\end{figure}

>>>>

\raft{two bits saved here (commented out): ad-hoc-ness of surrogate design, and BEP success story}

% Construction of surrogates for a desired task is often ad hoc, leaving consistency of such losses an open question.
% Depending on the data distribution, these inconsistent surrogates may actually yield predictions that do not correspond to the target task.

% For some tasks, it is possible to reduce the dimension of this surrogate prediction space without sacrificing consistency.  
% Consider the high-confidence classification presented by the abstain target loss~\citep{ramaswamy2012classification,ramaswamy2018consistent}.
% When trying to predict one of $n$ outcomes, the abstain loss is minimized by predicting the most likely outcome if it is likely enough, and ``abstaining'' from predicting otherwise.
% \citet{ramaswamy2016convex} present a convex surrogate, called the BEP loss, for the abstain target loss that takes as input a prediction whose dimension is logarithmic in the number of outcomes.
% The BEP loss is a high-dimensional generalization of the hinge loss so that outcome predictions are ``embedded'' into the corners of the $\pm 1$ hypercube, and abstaining is embedded to the origin.
% This BEP loss is consistent with respect to the target 0-1 modification $\ell^{abs}(r,y) = \Ind{r \not \in \{y,\bot\}} + (1/2) \Ind{r = \bot}$, and takes $\Theta(\log n)$-dimensional surrogate predictions, instead of $\Theta(n)$, as was used by previous consistent surrogates, e.g.~\citet{crammer2001algorithmic}.

@@

\begin{figure}[ht]
\begin{minipage}{0.45\linewidth}
	\centering
	\includegraphics[width=\linewidth]{tikz/fsd-bound.pdf}
	\caption{%Since the uniform distribution is in the relative interior of the simplex and the level set $\gamma_\bot$, 
          $\dim(\Sc_{\gamma_\bot}($\textbullet$)) = 2$ and $\dim(\Sc_{\gamma_\bot}({\color{blue}\star})) = 1$.}
	\label{fig:fsd-bound}
\end{minipage}
\hfill
\begin{minipage}{0.45\linewidth}
	\centering
	\includegraphics[width=\linewidth]{tikz/flats-bound.pdf}
	\caption{Any $1$-flat $F$ through \textbullet leaves $\gamma_\bot$.
	However, there is a $1$-flat containing ${\color{blue}\star}$ that is a subset of $\gamma_\bot$ and $\gamma_3$.
	}
	\label{fig:flats-bound}
\end{minipage}
\end{figure}
